### 2023-06-02 ARB/standards/work-in-progress/document/tex/standard/provided_classes.tex
add cyrillic.rexx, rename unicode.md to Unicode_Requirements.md

aljl=alj-3{]} alj+l{]}=a{[}j-2{]}+1; /* Index changes \emph{/ end j
a{[}4{]}=arg(1) a{[}5J=1 return 12.2.4.2 PULL{]}=a{[}j+4{]}-1; /} Index
changes */ end j return r

@@

coll.6 =
.relation\textsubscript{new}\textasciitilde{}``{[}J=''(''zwei'',
2)\sout{''{[}{]}=''('\,''drei'', 3)}''{[}J=''('vier'',
8)\textasciitilde\textasciitilde''J=''C''drei'',3) coll.7 =
.set\textasciitilde of(2, 3, 9){]}=tmpSupp\textasciitilde ITEM
tmpSupp\textasciitilde NEXT END do until hope hope=1 do j=1 to
k\textasciitilde dimension(1)-1 if
k{[}j{]}\textsubscript{string\textgreater k{[}j+1{]}}string \textbar,
(k{[}j{]}\textsubscript{string=k{[}j+1{]}}string \&
i{[}j{]}\textsubscript{string\textless i{[}j+1{]}}string) then do{]}=t
hope=0 end end end if O=collection\textasciitilde items then say'' The
result is empty!'' else do j=1 to k\textasciitilde dimension(1) SAY ''
'' ``index'' pp(k{[}j{]}) ``item'' ppd{[}j){]}=alj+1{]};a{[}j- 1
{]}=alj+2{]} end j

@@

/* Returns the last item in the list. \emph{/ if
a{[}1{]}/}ItemsCount\emph{/=0 then return .nil return
a{[}3\emph{a{[}1{]}/}ItemsCount*/+1 \textbar{]}
a{[}j+1{]}=al{[}j+4{]}-1; /} Index changes */ end j returm r

@@

/* Adds the object value to the queue at its tail. \emph{/
a=self\textasciitilde exposed a{[}1{]}/}ItemCount\emph{/=a{[}1
\textbar/}ItemCount*/+1
a{[}\{1+3\emph{a{[}1{]}/}ItemCount*/\textbar=arg(1)
a{[}2+3\emph{a{[}1{]}/}ItemCount\emph{/\textbar=al{[} 1 {]}/}ItemCount*/
return{]} r{[}n{]}=a{[}j+1{]} end j return
.supplier\textasciitilde new(m,r){]}=1

>>>>

aljl=alj-3{]} alj+l{]}=a{[}j-2{]}+1; /* Index changes */ end j
a{[}4{]}=arg(1) a{[}5J=1 return 12.2.4.2 PULL

::method pull /* Returns and removes the item at the head of the queue.
\emph{/ a=self\textasciitilde exposed if a{[}1{]}/}ItemCount\emph{/=0
then return .nil /} Stays empty \emph{/ r=a{[}4{]} a{[}1{]}
/}ItemCount\emph{/=a {[}1{]} /}ItemCount\emph{/-1 do j=4 by 3 to
1+3}a{[}1{]}/\emph{ItemCount}/ aljl=a{[}j+3{]} alj+l{]}=a{[}j+4{]}-1; /*
Index changes */ end j return r

@@

coll.6 =
.relation\textsubscript{new}\textasciitilde{}``{[}J=''(``zwei'',
2)\st{``{[}{]}=''('``drei'', 3)}``{[}J=''('vier'',
8)\textasciitilde\textasciitilde{}``J=''C''drei'',3) coll.7 =
.set\textasciitilde of(2, 3, 9)

coll.8 = .table\textsubscript{new}\textasciitilde{}``{[}{]}=''(``zwei'',
2)\st{``{[}J=''(``drei'', 3)}``{[}T{]}J=''C''vier'', 10)

coll.0 = 8

message. 1 = ``UNION''

message.2 = ``INTERSECTION'' \_\_/* index the same in both \emph{/
message.3 = ``DIFFERENCE'' /} if index only in Ist collection \emph{/
message.4 = ``XOR'' /} unique index among both collections \emph{/
message.5 = ``SUBSET'' /} target is subset of other collection */

message. = 5

target. = coll. hstart = 4 istart = \textbar{} jstart = 1

output = 1 setOfTargets = .set\textasciitilde new

SAY ``Test Results of Set Operations on Collection Classes -- dated''
date(`U')

SAY

DO h= hstart TO target.0 /* loop over target targetID =
target.h\textsubscript{class}id IF
\setOfTargets\textasciitilde hasindex(targetID) THEN DO SAY SAY
CENTER('' Target:'' targetID ````, 70,''=``)
setOfTargets\textasciitilde put(targetID) output = 1 END

DO i= istart TO coll.0 /* loop over other collections if output then do
output = 0 argumentID = coll.i\textsubscript{class}id SAY SAY CENTER(''
argument:'' argumentID ````, 65,''=``) SAY SAY''INPUT:'' SAY ``contents
of'' pp(targetID) ``target:'' CALL dump\_collection target.h SAY

SAY ``contents of'' pp(argumentID) ``argument:''

CALL dump\_collection colli

SAY

SAY CENTER('' start set operators ``, 65,''-``) end

DO j =jstart TO message.0 /* loop over set operators tmpString
\textbar{} = RIGHT(``h'' pp(h) ``i'' ppG) ``j'' ppG), 65)

*/

*/

*/

tmpString2 = pp(targetID ``\textasciitilde{}'' message.j
\textbar\textbar{} ``('' argumentID ``)'')

SAY OVERLAY ( tmpString2, tmpString1 )

/* set resume parameter in case of error*/

jstart = j+1 IF jstart\textgreater message.0 THEN DO istart = i+{]}

IF istart\textgreater coll.0 THEN DO hstart = h+1 istart = 1

END jstart = 1 output = \textbar{} END /* process method invocation */
IF target.h\textasciitilde hasmethod(message.j) THEN DO tmp =
.message\textasciitilde new(target.h, message.j, ``I'',
coll.i)\textasciitilde send if ``The String
class''=tmp\textsubscript{class}defaultname then do if
datatype(tmp,``B'') then do

if tmp then SAY'' Result is TRUE'' else SAY'' Result is FALSE'' end end
else CALL dump\_collection tmp END ELSE

SAY pp(targetID) ``does not have method \textasciitilde{}''
pp(message.j)

SAY LEFT(````, 40,''-``) END jstart = 1 END jstart = 1 istart = 1 output
= 1 END

RETURN

dump\_collection:procedure USE ARG collection k =
.array\textasciitilde new i= .array\textasciitilde new tmpSupp =
collection\textasciitilde supplier DO WHILE
tmpSupp\textasciitilde AVAILABLE
k{[}k\textasciitilde dimension(1)+1{]}=tmpSupp\textasciitilde INDEX
i\{i\textsubscript{dimension(1)+1{]}=tmpSupp}ITEM
tmpSupp\textasciitilde NEXT END do until hope hope=1 do j=1 to
k\textasciitilde dimension(1)-1 if
k{[}j{]}\textsubscript{string\textgreater k{[}j+1{]}}string \textbar,
(k{[}j{]}\textsubscript{string=k{[}j+1{]}}string \&
i{[}j{]}\textsubscript{string\textless i{[}j+1{]}}string) then do

t=k{[}j{]}sk(jJ=kUj+ 1 )sk{[}j+1{]}=t t=i{[}j)siG {]}=if+ Usifj+t{]}=t
hope=0 end end end if O=collection\textasciitilde items then say'' The
result is empty!'' else do j=1 to k\textasciitilde dimension(1) SAY ''
'' ``index'' pp(k{[}j{]}) ``item'' ppd{[}j)

end RETURN /* Auxiliary routines \emph{/ pp: RETURN ``{[}''
\textbar\textbar{} ARG(1)\textasciitilde string \textbar\textbar{} ``J''
{[}}

/* X3J18 Rexx Language Standard proposal for the Set-like operations on
the Collection classes */

/* Tn the same way that the first standard uses BIFs which are defined
using other BIFs and ultimately the arithmetic and character operators,
the second standard can define classes using other classes and some
fundamental basis.

This program gives the definition of some other classes, in a form which
(when thoroughly developed) might be part of the second standard. It
also has a testing mechanism, which will not be part of a standard.

This particular program is implementing collections on top of array. */

/* The class Collection is not one builtin, but is used to simplify the
definition. */

::class `Collection'

:imethod init expose a /* A collection is modelled as using 3 slots in
an array for each element. The first slot holds the item, the second the
index, and the third is used by particular types of collection. This
order of slots is arbitary, chosen to match order of arguments for PUT
and SUPPLIER\textasciitilde NEW. \emph{/ /} The first set of 3 slots is
reserved for other purposes, to avoid having separate variables which
the subclassing would need to access. \emph{/
a=.alray\textasciitilde new a{[}1{]}/}ItemsCount\emph{/=0
a{[}2{]}/}Unique*/=0

/* This method allows subclasses to get at the implementation of
Collection. */ retum a

::method findindex private expose a /* Returns array index if the
collection contains any item associated with the index specified or
returns 0 otherwise. \emph{/ do j=4 by 3 to
143}a{[}1{]}/\emph{ItemsCount}/ if a{[}j+1{]}==arg(1) then return j end
j return 0

::method at /* rANY \emph{/ expose a /} Returns the item associated with
the specified index. */ j=self\textasciitilde findindex(arg(1)) if j=0
then return .nil return a{[}j{]}

::method put /* rANY rANY \emph{/ expose a use arg item, index /}
Replaces any existing item associated with the specified index with the
new item. Otherwise adds the item-index pair. \emph{/
j=self\textasciitilde findindex(index) if j\textgreater0 then do
a{[}j{]}=item returm end a{[}1{]}/}ItemsCount\emph{/=a{[}1
{]}/}ItemsCount\emph{/+1 j=lt3}a{[}1{]}/\emph{ItemsCount}/ a{[}j{]}=item
a{[}j+1{]}=index a{[}j+2{]}=0 return /* Error 91 in OOI if context
requiring result. */

:method `{[}{]}=' /* Synonym for the PUT method. */

forward message `PUT'

z:method hasindex /* rANY \emph{/ /} Returns \textbar{} (true) if the
collection contains any item associated with the index specified or
returns O (false) otherwise. */

return self\textasciitilde findindex(arg(1))\textgreater0

zimethod remove /* rANY */

r=alj{]}

self\textasciitilde removeit(j)

returm r

do j=j+3 by 3 to 14+3\emph{a{[}1{]}/}ItemsCount*/
a{[}j-3{]}=alj{]};alj-2{]}=alj+1{]};a{[}j- 1 {]}=alj+2{]} end j

@@

/* Returns the last item in the list. \emph{/ if
a{[}1{]}/}ItemsCount\emph{/=0 then return .nil return
a{[}3}a{[}1{]}/\emph{ItemsCount}/+1 \textbar{}

::method next P* rANY \emph{/ a=self\textasciitilde exposed /} Returns
the index of the item that follows the list item having the specified
index. */

jait3

if j\textgreater3\emph{a{[}1{]}/}ItemsCount\emph{/ then return .nil /}
Next of last was requested. */

zimethod previous /* rANY */

ja-3

zimethod section /* rANY OoWHOLE\textgreater=0 \emph{/
a=self\textasciitilde exposed /} Returns a new list containing selected
items from the receiver list. The first item in the new list is the item
corresponding to the index specified, in the receiver list. \emph{/
j=self\textasciitilde findindex(arg(1)) if j=0 then call Raise
`Syntax',93.918 r=.list\textasciitilde new /} To build result in.
\emph{/ if arg(2,`E') then s = arg(2) else s =
self\textasciitilde items; do s r\textasciitilde insert(a{[}j{]}) jait3
if j\textgreater1+3}a{[}1{]}/\emph{ItemsCount}/ then leave end retum r

::class `Queue' subclass Collection /* A queue is a sequenced collection
with whole-number indexes. The indexes specify the position of an item
relative to the head (first item) of

the queue. Adding or removing an item changes the association of an
index to its queue item. */

::method push /* rANY */

/* Adds the object value to the queue at its head. \emph{/
a=self\textasciitilde exposed a{[}1{]}/}ItemCount\emph{/=a{[}1
\textbar/}ItemCount*/+1

aljl=alj-3{]} a{[}j+1{]}=a{[}j-2{]}+1; /* Index changes */ end j
a{[}4{]}=arg(1) a{[}5{]}=1 return ::method pull

/* Returns and removes the item at the head of the queue. \emph{/
a=self\textasciitilde exposed if a{[}1{]}/}ItemCount\emph{/=0 then
return .nil /} Stays empty \emph{/ r=a{[}4{]}
a{[}1{]}/}ItemCount\emph{/=a{[}1{]}/}ItemCount\emph{/- 1 do j=4 by 3 to
14+3}a{[}1{]}/\emph{ItemCount}/ alj\}=alj+3{]} a{[}j+1{]}=al{[}j+4{]}-1;
/* Index changes */ end j returm r

@@

/* Adds the object value to the queue at its tail. \emph{/
a=self\textasciitilde exposed a{[}1{]}/}ItemCount\emph{/=a{[}1
\textbar/}ItemCount\emph{/+1
a{[}\{1+3}a{[}1{]}/\emph{ItemCount}/\textbar=arg(1)
a{[}2+3\emph{a{[}1{]}/}ItemCount\emph{/\textbar=al{[} 1 {]}/}ItemCount*/
return

:imethod peek

zimethod remove /* rWHOLE\textgreater O \emph{/ /} Returns and removes
from a collection the member item with the specified index. \emph{/
a=self\textasciitilde exposed if
a{[}1{]}/}ItemCount\emph{/\textless arg(1) then return .nil
r=self\textasciitilde remove:super(arg(1)) /} Reset the indexes. \emph{/
k=0 do j=4 by 3 to 143}a{[}1{]}/\emph{ItemsCount}/ k=k+1 a\{j+1J=k

end j return r

::class ``Table' subclass Collection

::method union /* rCOLLECTION */ return CommonUnion(self,arg(1))

::method intersection /* rCOLLECTION \emph{/ /} Returns a new collection
of the same class as SELF that contains the items from SELF that have
indexes also in the argument. \emph{/ /} Actually an index in SELF can
only be `matched' with one in the argument once. */

return self\textsubscript{difference(self}difference(arg(1)))

::method xor /* rCOLLECTION \emph{/ /} Returns a new relation that
contains all items from self and the argument except that all index-item
pairs that appear in both collections are removed. */ return
CommonXor(self,arg(1))

::method subset = /* rCOLLECTION */ return
self\textsubscript{difference(arg(1))}items = 0

::class `Set' subclass table

/* A set is a collection that restricts the member items to have a value
that is the same as the index. Any object can be placed in a set. There
can be only one occurrence of any object in a set. */

/* Second arg same as first. Committee has dropped second? \emph{/
:rmethod put /} rANY oANY \emph{/ /} Makes the object value a member
item of the collection and associates it with specified index. \emph{/
if arg(2,`E') then if arg(2)==arg(1) then signal error /} 949 */
self\textasciitilde put:super(arg(1),arg(1))

zimethod of class /* 1 or more rANY \emph{/ /} Returns a newly created
set containing the specified value objects. */ r=self\textasciitilde new
do j=1 to arg() r\textasciitilde put(arg(j)) end j retum r

::method union /* rCOLLECTION */ return CommonUnion(self,EnBag(arg(1)))

::method intersection /* rCOLLECTION */ return
self\textsubscript{difference(self}difference(arg(1)))

::method xor /* rCOLLECTION */ return CommonXor(self,EnBag(arg(1)))

::method difference /* rCOLLECTION */ return
CommonDifference(self,EnBag(arg(1)))

::class `Relation' subclass Collection

::method put /* rANY rANY */

j=lt3\emph{a{[}1{]}/}ItemsCount*/

a{[}j{]}=item

a{[}j+1{]}=index

:imethod items /* oANY \emph{/ a=self\textasciitilde exposed /} Returns
the number of relation items with the specified index. If you specify

no index, this method returns the total number of items associated with
all indexes in the relation. */

if \arg(1,'E') then return a{[}1{]}/\emph{ItemsCount}/

n=0

do j=4 by 3 to 143\emph{a{[}1{]}/}ItemsCount*/

if arg(1)==a{[}j+1{]} then n=n+1 end j retum n

zimethod supplier /* oANY \emph{/ a=self\textasciitilde exposed /}
Returns a supplier object for the collection. If an index is specified,
the supplier enumerates all of the items in the relation with the
specified index. \emph{/ m=.array\textasciitilde new /} For the items
\emph{/ r=.array\textasciitilde new /} For the indexes \emph{/ do j=4 by
3 to 143}a{[}1{]}/\emph{ItemsCount}/ if arg(1,`E') then if
arg(1)==a{[}j+1{]} then iterate n=r\textasciitilde dimension(1)+1
m{[}n{]}=alj{]} r{[}n{]}=a{[}j+1{]} end j return
.supplier\textasciitilde new(m,r)

::method union /* rCOLLECTION \emph{/ /} Union for a relation is just
all of both. */ r=self\textsubscript{class}new
cs=self\textasciitilde supplier do while cs\textasciitilde available
r{[}cs\textasciitilde index{]}=cs\textasciitilde item
cs\textasciitilde next end cs=MayEnBag(arg(1))\textasciitilde supplier
do while cs\textasciitilde available
r{[}cs\textasciitilde index{]}=cs\textasciitilde item
cs\textasciitilde next end return r

::method intersection /* rCOLLECTION */ return
self\textsubscript{difference(self}difference(arg(1)))

::method xor /* rCOLLECTION */ return CommonXor(self,arg(1))

zimethod difference /* rCOLLECTION \emph{/ /} Returns a new relation
containing only those index-item pairs from the

163 SELF whose indexes the other collection does not contain. */
r=self\textsubscript{class}new cs=self\textasciitilde supplier do while
cs\textasciitilde available
r{[}cs\textasciitilde index{]}=cs\textasciitilde item
cs\textasciitilde next end cs=MayEnBag(arg(1))\textasciitilde supplier
do while cs\textasciitilde available
r\textsubscript{removeitem(cs}item,cs\textasciitilde index)
cs\textasciitilde next end return r

::method subset = /* rCOLLECTION */ return
self\textsubscript{difference(arg(1))}items = 0

zimethod removeitem /* rANY rANY \emph{/ a=self\textasciitilde exposed
/} Returns and removes from a relation the member item value (associated
with the specified index). If value is not a member item associated with
index index, this method returns the NIL object and removes no item.
\emph{/ do j=4 by 3 to 143}a{[}1{]}/\emph{ItemsCount}/ if a\{jJ==arg(1)
\& a{[}j+1{]}==arg(2) then do self\textasciitilde removeit(j) return
arg(1) end end j return .nil

:rmethod index /* rANY \emph{/ a=self\textasciitilde exposed /} Returns
the index for the specified item. If there is more than one index
associated with the specified item, the one this method returns is not
defined. \emph{/ do j=4 by 3 to 143}a{[}1{]}/\emph{ItemsCount}/ if
arg(1)==a{[}j{]} then return a{[}j+1{]} end j return .nil

::method allat /* rANY */

a=self\textasciitilde exposed /* Returns a single-index array containing
all the items associated with the specified index. */

r=.array\textasciitilde new

do j=4 by 3 to 143\emph{a{[}1{]}/}ItemsCount*/

if arg(1)==a{[}j+1{]} then r{[}r\textasciitilde dimension(1)+1{]} =
a{[}j{]} end j return r

::method hasitem /* rANY rANY \emph{/ a=self\textasciitilde exposed /}
Returns 1 (true) if the relation contains the member item value
(associated with specified index). Returns 0 (false) otherwise. \emph{/
do j=4 by 3 to 143}a{[}1{]}/\emph{ItemsCount}/ if a\{jJ==arg(1) \&
a{[}j+1{]}==arg(2) then return \textbar{} end j return 0

z:method allindex /* rANY \emph{/ a=self\textasciitilde exposed /}
Returns a single-index array containing all indexes for the specified
item. \emph{/ r=.array\textasciitilde new do j=4 by 3 to
143}a{[}1{]}/\emph{ItemsCount}/ if a{[}j{]}==arg(1) then do
r{[}r\textasciitilde dimension(1)+1{]}=a{[}j+1{]} end end j returm r

zimethod of class /* 1 or more rANY \emph{/ /} Returns a newly created
bag containing the specified value objects. */ r=self\textasciitilde new
do j=1 to arg() r\textasciitilde put(arg(j)) end j retum r

:rmethod put /* rANY oANY \emph{/ /} Committee does away with second
argument? \emph{/ /} Makes the object value a member item of the
collection and associates it with the specified index. If you specify
index, it must be the same as value. */ if arg(2,`E') then if
arg(2)==arg(1) then signal error
self\textasciitilde put:super(arg(1),arg(1))

/* Bag may be a subclass of relation but many methods have different
semantics. */

::method union /* rCOLLECTION */ return CommonUnion(self,EnBag(arg(1)))

::method intersection /* rCOLLECTION */ return
self\textsubscript{difference(self}difference(arg(1)))

::method xor /* rCOLLECTION */ return CommonXor(self,EnBag(arg(1)))

::method difference /* rCOLLECTION */ return
CommonDifference(self,EnBag(arg(1)))

/* Later we take three array elements for each element in the directory,
one for the item, one to contain the index, one to say if the item is a
method

to be run or not. */

::method at /* rANY \emph{/ a=self\textasciitilde exposed /} Returns the
item associated with the specified index. \emph{/
j=self\textasciitilde findindex(arg(1)) if j=0 then return .nil /} Run
the method if there is one. */ if a{[}j+2{]} then return
self\textasciitilde run(a{[}j{]}) return a{[}j{]}

::method put /* rANY rANY \emph{/ a=self\textasciitilde exposed /} Makes
the object value a member item of the collection and associates it with
the specified index. */ if
\arg(2)\textasciitilde hasmethod(MAKESTRING'\,') then call Raise
`Syntax', 93.938 self\textsubscript{put:super(arg(1),arg(2)}makestring)
return

:imethod supplier a=self\textasciitilde exposed

/* Returns a supplier object for the directory. */

/* Check out what happens to the SETENTRY fields. \emph{/
r=.array\textasciitilde new /} For items */

do j=4 by 3 to 143\emph{a{[}1{]}/}ItemsCount*/
r{[}r\textasciitilde dimension(1)+1{]}=a{[}j{]} end j

return .supplier\textsubscript{new(r,self}makearray)

::method union /* rCOLLECTION */ return CommonUnion(self,arg(1))

::method intersection /* rCOLLECTION */ return
self\textsubscript{difference(self}difference(arg(1)))

::method xor /* rCOLLECTION */ return CommonXor(self,arg(1))

::method subset = /* rCOLLECTION */ return
self\textsubscript{difference(arg(1))}items = 0

z:method setentry /* rSTRING oANY \emph{/ a=self\textasciitilde exposed
/} Sets the directory entry with the specified name (translated to
uppercase) to the second argument, replacing any existing entry or
method for the specified name. \emph{/ n=translate(arg(1))
j=self\textasciitilde findindex(n) if j=0 \& \arg(2,`E') then return if
\arg(2,`E') then do /} Removal \emph{/ self\textasciitilde removeit(j)
returm end if j=0 then do /} It's new \emph{/
a{[}1{]}/}ItemsCount\emph{/=a{[}1{]}/}ItemsCount\emph{/ +1
j=lt3}a{[}1{]}/\emph{ItemsCount}/ a{[}j+1{]}J=n end a{[}j{]}=arg(2)
a{[}j+2{]}=0

::method entry /* rSTRING */

a=self\textasciitilde exposed /* Returns the directory entry with the
specified name (translated to uppercase). */

j=self\textasciitilde findindex(n) /\emph{if j=0 then signal error
according to online }/ /* Online has something about running UNKNOWN.
\emph{/ if j=0 then return .nil /} Tf there is an entry decide whether
to invoke it. */ if a\textasciitilde hasindex(j) then do if \a[j+2] then
return a{[}j{]} return self\textasciitilde run(a{[}j{]}) end

z:method hasentry /* rSTRING \emph{/ /} Returns 1\textbar{} (true) if
the directory has an entry or a method for the specified name
(translated to uppercase) or O (false) otherwise. */

return self\textasciitilde findindex(translate(arg(1)))\textgreater0

z:method setmethod /* rSTRING oMETHOD \emph{/
a=self\textasciitilde exposed /} Associates entry with the specified
name (translated to uppercase) with method method. Thus, the language
processor returns the result of running method when you access this
entry. \emph{/ /} (Part of METHOD checking converts string or array to
actual method.) \emph{/ n=translate(arg(1))
j=self\textasciitilde findindex(n) if j=0 \& \arg(2,`E') then return if
\arg(2,'E') then do self\textasciitilde removeit(j) returm end if j=0
then do /} It's new \emph{/
a{[}1{]}/}ItemsCount\emph{/=a{[}1{]}/}ItemsCount\emph{/ +1
j=lt3}a{[}1{]}/\emph{ItemsCount}/ a{[}j+1{]}J=n end a{[}j{]}=arg(2)
a\{j+2{]}=1

### 2023-06-02 ARB/standards/work-in-progress/document/tex/standard/syntax_constructs.tex
add cyrillic.rexx, rename unicode.md to Unicode_Requirements.md

  occurrence of an ofher\_negator within Operator is supplied as '\,';

@@

When the lexical process recognizes tokens to be supplied to the top
level, there can be changes made or tokens added. Recognition is
performed by the lexical process and the top level process ina
synchronized way. The tokens produced by the lexical level can be
affected by what the top level syntax has recognized. Those tokens will
affect subsequent recognition by the top level. Both processes operate
on the characters and the tokens in the order they are produced. The
term ``context'' refers to the progress of the recognition at some
point, without consideration of unprocessed characters and tokens. If a
token which is `+', `-', ' or `(' appears in a lexical level context
(other than after the keyword `PARSE') where the keyword `VALUE' could
appear in the corresponding top level context, then `VALUE' is passed to
the top level before the token is passed. If an `=' operator\_char
appears in a lexical level context where it could be the `=' of an
assignment or message\_instruction in the corresponding top level
context then it is recognized as the `=``' of that instruction. (It will
be outside of brackets and parentheses, and any Var\_symbo/ immediately
preceding it is passed as a VAR\_SYMBOL). If an operand is followed by a
colon token in the lexical level context then the operand only is passed
to the top level syntax as a LABEL, provided the context permits a
LABEL. Except where the rules above determine the token passed, a
Var\_symbol is passed as a terminal (a keyword) rather than as a
VAR\_SYMBOL under the following circumstances:

@@

raise \textbar{} reply \textbar{} return \textbar{} say \textbar{}
signal \textbar{} trace \textbar{} use `THEN' Msg8.1 `ELSE' Msg8.2
`WHEN' Msg9.1 \textbar{} `OTHERWISE' Msg9.2 command = expression address
= `ADDRESS' {[}(taken constant {[}expression{]}{]}

@@

power expression multiplicative operator:= '*' \textbar{} `/' \textbar{}
`//' \textbar{} `\%! power expression := prefix expression \textbar{}
power expression'**' prefix expression prefix expression := (`+'
\textbar{} `-' \textbar{} '\,') prefix expression term \textbar{}
Msg35.1 /* ``Stub'' has to be identified semantically? */

>>>>

  occurrence of an ofher\_negator within Operator is supplied as
  '\textquotesingle;

@@

When the lexical process recognizes tokens to be supplied to the top
level, there can be changes made or tokens added. Recognition is
performed by the lexical process and the top level process ina
synchronized way. The tokens produced by the lexical level can be
affected by what the top level syntax has recognized. Those tokens will
affect subsequent recognition by the top level. Both processes operate
on the characters and the tokens in the order they are produced. The
term ``context'' refers to the progress of the recognition at some
point, without consideration of unprocessed characters and tokens. If a
token which is `+', `-', \textquotesingle{} or `(' appears in a lexical
level context (other than after the keyword `PARSE') where the keyword
`VALUE' could appear in the corresponding top level context, then
`VALUE' is passed to the top level before the token is passed. If an `='
operator\_char appears in a lexical level context where it could be the
`=' of an assignment or message\_instruction in the corresponding top
level context then it is recognized as the `=``' of that instruction.
(It will be outside of brackets and parentheses, and any Var\_symbo/
immediately preceding it is passed as a VAR\_SYMBOL). If an operand is
followed by a colon token in the lexical level context then the operand
only is passed to the top level syntax as a LABEL, provided the context
permits a LABEL. Except where the rules above determine the token
passed, a Var\_symbol is passed as a terminal (a keyword) rather than as
a VAR\_SYMBOL under the following circumstances:

@@

raise \textbar{} reply \textbar{} return \textbar{} say \textbar{}
signal \textbar{} trace \textbar{} use `THEN' Msg8.1 `ELSE' Msg8.2
`WHEN' Msg9.1 \textbar{} `OTHERWISE' Msg9.2 command = expression address
= `ADDRESS' {[}(taken constant {[}expression{]}

Msg19.1 \textbar{} valueexp) {[} `WITH' connection{]} {]}

@@

power expression multiplicative operator:= '*' \textbar{} `/' \textbar{}
`//' \textbar{} `\%! power expression := prefix expression \textbar{}
power expression'**' prefix expression prefix expression := (`+'
\textbar{} `-' \textbar{} '\textquotesingle) prefix expression term
\textbar{} Msg35.1 /* ``Stub'' has to be identified semantically? */
